\documentclass[10pt]{extarticle}
%\documentclass[]{file}
\usepackage[margin=0.2in]{geometry}
\usepackage{romannum}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!50,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
    }
\begin{document}
\begin{flushleft}
\centering {\huge\textbf{SHUBHAM KUMAR}}
\end{flushleft}
\textbf {Email : }{Nimcetshubhamkumar@gmail.com}
\hfill\textbf {GitHub :} \href{https://github.com/ShubhamKumar1996}{https://github.com/ShubhamKumar1996}
\hfill\textbf {Mobile : }+91-9805764114
\vspace{-10pt}\\
{\large \textbf{\begin{tcolorbox}\textsc{Technical Skills}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Programming Languages: }C++ (Proficient), Java (Intermediate), Python (Beginner), Server-Side JavaScript (Beginner).
\vspace{1mm}
\item \textbf{Tools \& Frameworks: }Node.js, Express.js, MongoDB, SQL, VS Code, Git \& GitHub, Jupyter Notebook, Spyder IDE.
\vspace{1mm}
\item \textbf{Coursework: }Data Structure \& Algorithms, Object-Oriented Programming, Database Systems, Operating System.
\vspace{1mm}
\end{itemize}
\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Key Projects}\end{tcolorbox}}}
\begin{itemize}
\item \href{https://github.com/ShubhamKumar1996/Worth_IT-Web_Application}{\textbf{Worth-IT Web Application}}\hfill\hfill(\textit{Jan'20- Ongoing})

\\\textbf{Tool \& Framework Utilized: }Node.js, Express.js, MongoDB, Mongoose, HTML, CSS.
\begin{itemize}
\item Developed an \textbf{E-commerce Web Application} using Node.js which allows an authenticated user to buy products. 
\item Enabled the users to create and sign in to secure \textbf{Sessions}. 
\item Used \textbf{MongoDB} as the real-time database manager and \textbf{Mongoose} as a Object Document Mapping Tool.
\item Implemented \textbf{User Authentication} by restricting unauthorized user to gain access to restricted routes.
\item Protection from \textbf{Cross-Site Request Forgery (CSRF) Attacks}.
\item Implemented \textbf{Authorization} by allowing only authorized user to update \& delete product.
\end{itemize}
\vspace{1mm}
\item \href{https://github.com/ShubhamKumar1996/Twitter_Sentiment_Analysis_Tool}{\textbf{Twitter Sentiment Analysis Tool}} \hfill\hfill(\textit{Aug'20-Sep'20})
\\\textbf{Library Utilized: }Logistic Regression, NLTK, SKlearn, Tweepy, Matplotlib, Numpy, Twitter API.
\begin{itemize}
\item This tool help us in collecting insights about particular keywords from twitter.
\item Collects all recent tweets which consists of mentioned keywords from twitter and perform Sentiment Analysis on them.
\item Used TF-IDF vectorizer for converting text from dataset into vectors.
\item Logistic Regression is used for training model.
\item Used Confusion matrix for comparing predicted result with actual result.
\item Achieved approx 85\% accuracy.
\end{itemize}
\vspace{2mm}
\item \href{https://github.com/ShubhamKumar1996/REST-API}{\textbf{RESTful API}}\hfill\hfill(\textit{Apr'19-Ongoing})
\\\textbf{Tool \& Framework Utilized: }Node.js, Express.js, MongoDB, Mongoose, Postman.
\begin{itemize}
\item Developed REST API with Create, Retrieve, Update, and Delete \textbf{(CRUD) functionalities} using Node.js, Express.js framework, Mongoose (ODM) to interact with MongoDB and Postman to test API with requests.
\end{itemize}
\vspace{2mm}
\item \href{https://github.com/ShubhamKumar1996/Web-Scrapper}{\textbf{Web Scrapper}}\hfill\hfill(\textit{Jun'19-Jul'19})
\\\textbf{Library Utilized: }Beautiful Soup, Requests, Csv.
\begin{itemize}
\item A simple web Scrapper which scrapes Heading or Title, Video Link and Summary of each post from http://coreyms.com and then save all  these details in CSV file.
\end{itemize}
\end{itemize}

{\large \textbf{\begin{tcolorbox}\textsc{Scholastic Achievements}\end{tcolorbox}}}
\begin{itemize}
\item Secured \textbf{All India Rank 76} in \textbf{NIMCET 2018} which is a National Level Entrance Exam.
\vspace{1mm}
\item Recieved the \textbf{Best Performer Award} in Nakshtra'20 Technical Fest organized by NIT Calicut.
\vspace{1mm}
\item Among \textbf{Top 50} Coders in InterviewBit, GeeksforGeeks at University Level.
\vspace{1mm}
\item Secured \textbf{First Position} in Code Chamber event in Version'19 which is a Technical Fest Organized by NIT Tiruchirappalli.
\vspace{1mm}
\item Contributed in \textbf{First Position} of Cricket team in Inter-Branch Cricket Tournament 2020 at NIT Karnataka.
\end{itemize}

\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Academic Qualifications}\end{tcolorbox}}}
\begin{center}
\begin{tabular}{|p{2.5cm}|p{6.0cm}|p{8.5cm}|p{1.8cm}|}
\hline
\centering{\textbf{Year}} & \centering{\textbf{Degree/Certificate}} & \centering{\textbf{Institute}} & \textbf{CGPA/$\%$}\\
\hline
\centering{2018} - Present & \centering{MCA} & \centering{National Institute of Technology, Karnataka} & 7.7/10\\
\hline
\centering{2018} & \centering{BCA} & \centering{Dr. Y.S Parmar P.G College, Nahan} & 7.0/10\\
\hline
\centering{2014} & \centering{CBSE(\Romannum{12})} & \centering{ Jawahar Navodaya Vidyalaya, Nahan} & 75$\%$\\
\hline
\centering{2012} & \centering{CBSE(\Romannum{10})} & \centering{ Jawahar Navodaya Vidyalaya, Nahan} & 74$\%$\\
\hline
\end{tabular}
\end{center}

\vspace{1mm}
{\large \textbf{\begin{tcolorbox}\textsc{Positions of Responsibility}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Active Member of Mind Fuel Club}\hfill\hfill(\textit{2018-present})
\begin{itemize}
\item Mind Fuel Club is club allow us to help students in getting started with Competitive Programming.
\end{itemize}
\vspace{1mm}
\item \textbf{Core Member of IGNITE'20}\hfill\hfill(\textit{Mar'19-Apr'19})
\begin{itemize}
\item IGNITE is a All India MCA Meet in which MCA students from colleges across India come together and participate in Technical Fest.
\end{itemize}
\vspace{4mm}
\end{itemize}
%\medskip
%\newpage
%\end{itemize}

\end{document}